An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-30 Article/EconGrowth2.Rnw
EconGrowth2.Rnw now uses loadResampledData function for the CD ternary plot.

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- Econ2011

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
oModels <- readRDS(f)
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none", baseResample=baseResample)
  dataCDQ <- loadAllResampleData(modelType="cde", countryAbbrevsOrder=countryAbbrevs, energyType="Q", baseResample=baseResample)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

>>>>

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
# baseHistorical <- file.path("..", "data")
historicalData <- Econ2011 # From the EconData package

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-04-29_Refactored-EconData_n=2.zip")
# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(archive, file.path("oModels.Rdata")))
oModels <- readRDS(f)
close(f)

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
data <- loadResampledData(archive=archive, 
                          country=countryAbbrevs, 
                          model="cd", 
                          factors=c("iK+iL", "iK+iL+iQ"), 
                          prefix="coeffs")
# Rearrange the factors to obtain our preferred ordering of countries.
for (l in rev(countryAbbrevs)) { data$countryAbbrev <- relevel(data$countryAbbrev, ref=l) }
# Replace all NA's in energyType with "none"

# Rearrange the factors to obtain our preferred ordering of countries.

for (l in rev(energyTypes)) { data$energyType <- relevel(data$energyType, ref=l) }
standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
@
